\newpage
\chapter*{Acknowledgements}
This semester project would not be possible without the help of my supervisors, Cyprien Hoelzl and professor Eleni Chatzi. I first reached out to Eleni for a semester project opportunity during ETH week -- for the purpose of improving my skills in doing research. Shortly therafter, I was introduced to her PhD student, Cyprien Hoelzl, about a project revolving around identifying and classiying defects on train tracks.

Cyprien has been an exceptional mentor throughout this entire project. I received all the acdemic guidance necessary and whenever I had issues, I could always drop by his office or text him, after which helpful answers would promptly ensue. From the beginning, I could tell that he is down-to-earth, very intelligent and possess great specialization in the field of train maintenance and monitoring. He is very good at explaining difficult concepts (with his quick and intuitive hand-drawings) and provided me with many informative resources. Furthermore, he truly cared about my progress, goes out of his way to aid me, and provides constructive feedback for everything I present to him. 

Eleni has also been very supportive about my progress, always arranging intermediate update sessions and staying on top of the project. These have been a great driver in keeping me accountable and making further progress. Eleni is very approachable, kind, and great at providing feedback at the intermediate update sessions. She is extremely active in her endeavours and one can that she is an expert in the field of Structural Health Monitoring (among others).

Finally, I greatly appreciate the help that I have received from Eleni's other PhD student, Harry (Mylonas Charilaos). He has provided me with very informative tools/feedback for my work with neural network architectures. Although interactions were few, one can immediately tell that he is very knowledgeable about the field of machine learning.
 
I have great gratitude for this opportunity working alongside Eleni and her multi-talented team. It has been a pleasant and educational experience. I sincerely could not ask for better supervisors.


\newpage


